Concurrent Programming in Harmony

### 2021-12-24 book/paper.tex
Started working on deadlock chapter

Imagine five philosopers sitting around a table, each with a plate of food in
front of them and a fork between every two plates.  Each philosopher requires
two forks to eat.  To start eating, a philosopher first picks up the fork on
the left, then the fork on the right.  Each philosopher likes to take breaks
from eating to think for a while.  To do so, the philosopher puts down both
forks.  Each philosopher repeats this procedure.  Dijkstra had them repeating
this for ever, but for the purposes of this book, philosophers can leave
the table when they are not using any forks.

@@

\vspace{1em}
\begin{code}
<{:input:../code/dinersfix.hny}>
\end{code}
\vspace{1em}

@@

\vspace{1em}
\begin{code}
<{:input:../code/dinersfix2.hny}>
\end{code}
\vspace{1em}

>>>>

Imagine five philosopers sitting around a table, each with a plate of food in
front of them and a fork between every two plates.  Each philosopher requires
two forks to eat.  To start eating, a philosopher first picks up the fork on
the left, then the fork on the right.  Each philosopher likes to take breaks
from eating to think for a while.  To do so, the philosopher puts down both
forks.  Each philosopher repeats this procedure.  Dijkstra had them repeating
this for ever, but for the purposes of this book,
philosophers can---if they wish---leave the table when they are
not using any forks.

@@

\vspace{1em}
\begin{code}
<{:inline:}>
if left < right:
    synch.acquire(?forks[left])
    synch.acquire(?forks[right])
else:
    synch.acquire(?forks[right])
    synch.acquire(?forks[left])
<{:end:}>
\end{code}
\vspace{1em}

@@

\vspace{1em}
\begin{code}
<{:inline:}>
synch.acquire(?forks[min(left, right)])
synch.acquire(?forks[max(left, right)])
<{:end:}>
\end{code}
\vspace{1em}
